Displacement effects and implications of Large-Scale Marine Protected Areas

### 2018-09-14 rmd/Manuscript.Rmd
Updated file

```{r, echo = F}
suppressPackageStartupMessages({
  library(startR)
  library(tidyverse)
})

@@

```{r, echo = F}
vessel_info_pipa <- read.csv(here::here("data", "vessel_info_mmsi_inside_pipa.csv"), stringsAsFactors = F) %>% 
  mutate(treated = T)

vessel_info_pna <- read.csv(here::here("data", "vessel_info_mmsi_inside_pna.csv"), stringsAsFactors = F) %>% 
  mutate(treated = F)

vessel_info <- rbind(vessel_info_pipa, vessel_info_pna) %>% 
  rename(gear = inferred_label)

pipa_vessels <- read.csv(here::here("data", "vessels_inside_pipa.csv"))

@@

```{r}
effort_by_vessel <- read.csv(here::here("data", "pipa_effort_by_vessel.csv"), stringsAsFactors = F) %>% 
  rbind(read.csv(here::here("data", "pna_vessels_outside_pipa.csv"), stringsAsFactors = F)) %>% 
  left_join(vessel_info, by = c("mmsi", "year")) %>% 
  filter(gear %in% c("purse_seines", "drifting_longlines")) %>%
  mutate(mmsi = as.character(mmsi),
         month = as.character(month),
         year = as.character(year))

effort_by_vessel %>%  
  group_by(gear, treated, post) %>% 
  summarize(hours = mean(hours, na.rm = T)) %>% 
  spread(post, hours) %>% 
  mutate(change = `TRUE` / `FALSE`) %>% 
  knitr::kable(col.names = c("Gear", "Treated", "Before", "After", "Change (A / B)"),
               caption = "Mean fishing hours for each gear before and after")
```

@@

@@

- Divide pipa vessels by type of boat (longline vs. purse seine)
- Identify two counterfactuals:
    - A:
        - PNA
        - similar vessel
        - never fished inside PIPA
    -B:
        - Taiwan
        - Never in PNA
        - Similar region?

Has effort increased?

- Change in fishing hours before vs after
- Change in total hours before vs after
- Change in distance before vs after
- Where do PIPA vessels go?
- How many were transient vs local?

Has search time increased?

- Distance between fishing points before vs. after
- Prop hour fishing before vs after
- Time between fishing points before vs. after

@@

```{r, echo = F, fig.cap = "\\label{fig:blue_para}Monthly hours, number of vessels, and data points observed inside PIPA. These clearly show the blue-paradox effect."}
# This is just to show the blue paradox, no need to include this figure
pipa_vessels %>% 
  group_by(year, month, mmsi) %>% 
  summarize(n_points = sum(n_points),
            hours = sum(total_fishing_hours)) %>% 
  group_by(year, month) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_points = sum(n_points),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/")),
         post = year >= 2015) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post)) %>% 
  ggplot(aes(x = date, y = value)) +
  geom_line() +
  geom_point(aes(color = post)) +
  facet_wrap(~variable, scales = "free", ncol = 2) +
  theme_bw() +
  scale_color_brewer(palette = "Set1")
```

@@

```{r, echo = F, fig.cap = "\\label{fig:kir_vessels}Fishing hours and number of 12 Kiribati vessels from 2012 - 2016 that at some point fished inside PIPA."}
effort_by_vessel %>% 
  filter(kir, treated) %>% 
  group_by(year, month, mmsi, gear) %>% 
  summarize(hours = sum(hours)) %>% 
  group_by(year, month, gear) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/")),
         post = year >= 2015) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post, gear)) %>% 
  ggplot(aes(x = date, y = value)) +
  geom_line() +
  geom_point(aes(color = post)) +
  facet_wrap(gear~variable, scales = "free_y", ncol = 3) +
  theme_bw() +
  scale_color_brewer(palette = "Set1")
```

```{r, results = "asis", echo = F}
kir_vessel <- effort_by_vessel %>% 
  filter(kir, gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1)

m1 <- lm(hours ~ post*treated, data = kir_vessel)
m2 <- lm(hours ~ post*treated + month, data = kir_vessel)
m3 <- lm(hours ~ post*treated + month + year, data = kir_vessel)
m4 <- lm(hours ~ post*treated + month + year + mmsi, data = kir_vessel)

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("mmsi", "year", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Year FE", "No", "No", "Yes", "Yes"),
                                      c("Vessel FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "\\label{tab:kir_vessels}Fishing hours from GFW for vessels flying Kiribati flag (n = 12). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
```

@@

```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels that fished inside PIPA at least once."}
effort_by_vessel %>% 
  group_by(year, gear, treated, post, month) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
  ggplot(aes(x = date, y = value, group = treated)) +
  geom_line(aes(linetype = treated)) +
  geom_point(aes(color = post)) +
  facet_wrap(gear~variable, scales = "free", ncol = 3) +
  theme_bw() +
  scale_color_brewer(palette = "Set1")
```

@@

model_data <- effort_by_vessel %>% 
  filter(gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1) %>% 
  mutate_at(.vars = vars(month, year, mmsi), .funs = as.character)

m1 <- lm(hours ~ post*treated, data = effort_by_vessel)
m2 <- lm(hours ~ post*treated + month, data = effort_by_vessel)
m3 <- lm(hours ~ post*treated + month + year, data = effort_by_vessel)
m4 <- lm(hours ~ post*treated + month + year + mmsi, data = effort_by_vessel)

@@

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("mmsi", "year", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Year FE", "No", "No", "Yes", "Yes"),
                                      c("Vessel FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "\\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.")

```

```{r, echo = F}
map_df(models, broom::tidy, .id = "model") %>%
  filter(term %in% c("(Intercept)", "postTRUE", "treatedTRUE", "postTRUE:treatedTRUE")) %>%
  ggplot(aes(x = model, y = estimate)) +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
                size = 1,
                width = 0,
                color = "red") +
  geom_point(color = "steelblue", size = 3) +
  facet_wrap(~term, scale = "free") +
  theme_bw()
```

>>>>

```{r, echo = F, message = F, warning = F}
suppressPackageStartupMessages({
  library(startR)
  library(tidyverse)
})

@@

Number of vessels

Explain BACI strict

Analyses being run

Correct number of vessels in tables

Add figure legends

```{r}
effort_by_vessel <- read.csv(file = here::here("data", "effort_by_vessel.csv"))
```

```{r}
# Just to get pipa vessels that fished inside pipa before 2015
pipa_vessels <- read.csv(here::here("data", "vessels_inside_pipa.csv"))

@@

@@

```{r}
effort_by_vessel %>%
  filter(baci_strict) %>%
  group_by(gear, treated, post) %>% 
  summarize(hours = mean(hours, na.rm = T)) %>% 
  spread(post, hours) %>% 
  mutate(change = `TRUE` / `FALSE`) %>% 
  knitr::kable(col.names = c("Gear", "Treated", "Before", "After", "Change (A / B)"),
               caption = "Mean fishing hours for each gear before and after")
```

@@

- [x] Divide pipa vessels by type of boat (longline vs. purse seine)
- [x] Identify two counterfactuals:
    -  [x] A: PNA, similar vessel, never fished inside PIPA
    - [ ] B: Taiwan, Never in PNA, Similar region
- [x] Change in fishing hours before vs after
- [ ] ~~Change in total hours before vs after~~
- [ ] Change in distance before vs after
- [ ] Where do PIPA vessels go?

@@

```{r, echo = F, fig.cap = "\\label{fig:blue_para}Monthly hours, number of vessels, and data points observed inside PIPA. These clearly show the blue-paradox effect.", fig.height = 3, fig.width = 6}
# This is just to show the blue paradox, no need to include this figure
pipa_vessels %>% 
  group_by(year, month, mmsi) %>% 
  summarize(n_points = sum(n_points),
            hours = sum(total_fishing_hours)) %>% 
  group_by(year, month) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_points = sum(n_points),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/")),
         post = year >= 2015) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post)) %>% 
  ggplot(aes(x = date, y = value)) +
  geom_line() +
  geom_point(aes(color = post)) +
  facet_wrap(~variable, scales = "free", ncol = 2) +
  theme_bw() +
  scale_color_brewer(palette = "Set1")
```

@@

@@

```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels that fished inside PIPA at least once."}
effort_by_vessel %>% 
  filter(baci_strict) %>%
  group_by(year, gear, treated, post, month) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
  ggplot(aes(x = date, y = value, group = treated)) +
  geom_line(aes(linetype = treated)) +
  geom_point(aes(color = post)) +
  facet_wrap(gear~variable, scales = "free", ncol = 3) +
  theme_bw() +
  scale_color_brewer(palette = "Set1")
```

## Purse seiners

@@

model_data <- effort_by_vessel %>% 
  filter(baci_strict,
         gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1) %>% 
  mutate_at(.vars = vars(month, year, mmsi), .funs = as.character)

m1 <- lm(hours ~ post*treated, data = model_data)
m2 <- lm(hours ~ post*treated + month, data = model_data)
m3 <- lm(hours ~ post*treated + month + year, data = model_data)
m4 <- lm(hours ~ post*treated + month + year + flag, data = model_data)

@@

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("flag", "year", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Year FE", "No", "No", "Yes", "Yes"),
                                      c("Flag FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "\\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.")

map_df(models, broom::tidy, .id = "model") %>%
  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
  ggplot(aes(x = model, y = estimate)) +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
                size = 1,
                width = 0,
                color = "red") +
  geom_point(color = "steelblue", size = 3) +
  facet_wrap(~term, scale = "free") +
  theme_bw()
```

## Longliners

```{r, results = "asis"}

model_data <- effort_by_vessel %>% 
  filter(baci_strict,
         !gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1) %>% 
  mutate_at(.vars = vars(month, year, mmsi), .funs = as.character)

m1 <- lm(hours ~ post*treated, data = model_data)
m2 <- lm(hours ~ post*treated + month, data = model_data)
m3 <- lm(hours ~ post*treated + month + year, data = model_data)
m4 <- lm(hours ~ post*treated + month + year + flag, data = model_data)

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("flag", "year", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Year FE", "No", "No", "Yes", "Yes"),
                                      c("Flag FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "\\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.")

map_df(models, broom::tidy, .id = "model") %>%
  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
  ggplot(aes(x = model, y = estimate)) +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
                size = 1,
                width = 0,
                color = "red") +
  geom_point(color = "steelblue", size = 3) +
  facet_wrap(~term, scale = "free") +
  theme_bw()
```
